\include{./includes/minimal_boilerplate_000_}

\begin{document}

\normalFont \engrus
{\bf Wylie Kulik}
\\ Tel Aviv
\sectionSep
\\ {\bf contact:}
\\ email: yari.ashi.zero@yandex.com
\\ GitHub: \href{https://github.com/kulicuu}{kulicuu}
\\ website: \href{https://yari-ashi-zero.herokuapp.com/professional}{yari-ashi-zero.herokuapp.com/professional}
% \\ Professional Website: \href{https://yari-ashi-zero.herokuapp.com/professional}{yari-ashi-zero.herokuapp.com/professional}
% \\ \href{}{tech blog}
% \\ \href{}{portfolio}

\sectionSep
{\bf summary:}
\\ Fullstack web programmer. Focus: JavaScript, NodeJS, Redis, ReactJS.

\sectionSep
{\bf skills:}

Expert: JavaScript(CoffeeScript or Babel flavours), NodeJS/npm ecosystem (incl. NW.js \& electron), Redis(including Lua), ReactJS, programmatic SVG, HTML/CSS, AJAX, WebSockets.
\\ Moderate: Mobile native (ReactNative and AndroidNative), WebRTC, WebGL \& OpenGL, Python, Ruby, PostgreSQL, MongoDB, Linux sys-admin.
\\ Light (but interested): Haskell, Clojure, Cassandra, Apache Kafka, C++, Objective-C \& iOS.

\sectionSep
{\bf education:}
\\ In general mostly autodidactic \& holistic -- reading and nomadic travelling having taken up a substantial portion of my young adult life. Some institutional educational experience also: Mathematics studies 2007-10: Univ. Massachusetts, Boston (2009-10 exchange): Univ. Connecticut, Storrs 2003-2005: George Mason Univ., Virginia 1999-2000: Santa Monica College, CA; Completed most upper-level undergrad BSc maths requirements, left without degree. All said, continuous learning is a principle and way of life. I remain active in maths and computer science theoretical work, on my own time and for my own satisfaction.

\sectionSep
{\bf experience:}
\\ 20 years programming in amateur \& academic context: DOS hacking as youth, TurboPascal in high-school. Self-taught Java in 2000, Ruby and Python in 2007, Rails in 2010.
4 years programming in professional context: NodeJS, Angular, WebSockets, Redis, and React. In 2014 I built, deployed, and documented API for a social-economy application Bartr (Tel Aviv startup) with NodeJS, Redis, WebSockets, and Angular. In 2014-2015 I worked remotely for several startups in California implementing microservices, web-scaping modules, GUI components, and testing infrastructure. In 2015 I invented a new way to compose GUIs relying heavily on programmatic SVGs rather than HTML/CSS. Recently I've been developing games with React and WebGL, learning new languages Clojure and Haskell.



\end{document}
